---
title: "sharekhan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sharekhan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ShareKhan)
```

ShareKhan API is a collection of HTTPS-REST APIs that provide integration with our in-house trading
platform with which you can build your own customized trading applications.You can use the endpoints
to :

- Place, modify and cancel orders.
- Query specific order details, as well query holdings, positions, reports.
- Scrip Master which provides provides only active scrips for the day.
- Historical data and Websocket streaming


## Requirements

The use of the API is based on authentication, using `api_key`,`login id`,`password`,`secret key` 

## Workflow

The workflow starts with the creation of a sharekhan connect object and completing a successful login flow. 
To create a sharekhanconnect object the following may be used. 
The login url then may be obtained using the `get_login_url` function.

```r
connect = create_connection_object(params)
login_url = get_login_url(connect)
print(login_url)
```

Navigating to this login url and completing a successful login will generate a `request_token`. 
A successful login comes back with the `request_token` as a URL query parameter to the redirect URL registered on the 
(LOGIN_URL) for that `api_key`.

## API Handshake

Once the `request_token` is available, the `set_request_token` function can be used to update the sharekhan connect object and then call the `fetch_access_token` to complete the API handshake and obtain an `access_token`. A successful handshake will set the `access_token` slot inside the sharekhan connect object and return the object itself. From this point onward the handshake is complete and the API functions are available to the user.

```r
connect = set_request_token(connect,request_token)
connect = fetch_access_token(connect)
```

## Example of Use
The following displays the call signatures for some useful functions.

new_order_response <- place_order(connect, new_order_method_params)
modify_response <- modify_order(connect, modify_method_params)
cancel_response <- cancel_order(connect, cancel_method_params)
report_day_response <- get_report_day(connect, report_method_params) (Orders History)
trade_position_response <- get_trade_position(connect, trade_params) (Trades History)
order_history_response <- get_report_history(connect, order_method_params) (Order History)
report_trade_response <- get_report_trade(connect, report_method_params) (Trade History)
holdings_response <- get_holdings(connect, holdings_params)
master_response <- get_master(connect, master_params)
historical_reaponse <- get_historical(connect, historical_method_params)

`WebSocket`
socketObject <- sharekhan_connect_object(params)
sharekhanSocket.connect(socketObject)


